Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/background.tex
Paper update

We handle the scenarios where the topology of the analog circuit is fixed. This
is practical as there are usually a lot of classical topologies for given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters. This problem can then be formulated as a bound-constrained
black-box optimization problem:
\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x}),
\end{equation}
where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric of noisy
depending on the design specifications. Given the design parameters $\bm{x}$,
the FOM value can be obtained by commercial circuit simulators like HSPICE or
Spectre.

@@

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel, and a constant mean function
$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
objective function evaluations are noisy and let GP to infer the noise level
$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
numerical stability.

@@

The PI and EI functions are defined as
\begin{equation}
    \label{eq:PI_EI}
    \begin{array}{lll}
        \mathrm{PI}(\bm{x}) &=& \Phi(\lambda) \\
        \mathrm{EI}(\bm{x}) &=& \sigma(\bm{x}) (\lambda \Phi(\lambda) + \phi(\lambda))     \\
        \mathrm{\lambda}    &=& \displaystyle \frac{\tau - \xi - \mu(\bm{x})}{\sigma(\bm{x})},
    \end{array}
\end{equation}
where $\tau$ is the current best value objective value, and $\xi$ is a small positive jitter to improvement the ability of exploration. The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution. We fix $\xi = 1e-3$ in our implementation of the MACE algorithm.

>>>>

We handle the scenarios where the topology of the analog circuit is fixed. This
is practical as there are usually a lot of classical topologies for a given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters. This problem can then be formulated as a bound-constrained
black-box optimization problem:
\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x}),
\end{equation}
where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric or noisy
depending on the design specifications. Given the design parameters $\bm{x}$,
the FOM value can be obtained by commercial circuit simulators like HSPICE or
Spectre.

@@

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel~\cite{GPML}, and a constant
mean function $m(\bm{x}) = \mu_0$ for all our experiments. By default, we
assume the objective function evaluations are influenced by i.i.d. noise
$\epsilon_t \sim N(0, \sigma_n^2)$ and set the noise level $\sigma_n^2$ as a
hyperparameter.  The introduction of the i.i.d noise also helps to improve the
numerical stability.

@@

The PI and EI functions are defined as
\begin{equation}
    \label{eq:PI_EI}
    \begin{array}{lll}
        \mathrm{PI}(\bm{x}) &=& \Phi(\lambda) \\
        \mathrm{EI}(\bm{x}) &=& \sigma(\bm{x}) (\lambda \Phi(\lambda) + \phi(\lambda))     \\
        \mathrm{\lambda}    &=& \displaystyle \frac{\tau - \xi - \mu(\bm{x})}{\sigma(\bm{x})},
    \end{array}
\end{equation}
where $\tau$ is the current best value objective value, and $\xi$ is a small positive jitter to improvement the ability of exploration. The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution. In our implementation of the MACE algorithm, we fix $\xi$ = 1e-3.
